\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
%\usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Joel Daniel Rico} \\ \vspace{1pt}
    \small \href{mailto:joeldanielrico@csu.fullerton.edu.com}{\underline{joeldanielrico@csu.fullerton.edu}} $|$ 
    \href{https://linkedin.com/in/joeldanielrico}{\underline{linkedin.com/in/joeldanielrico}} $|$
    \href{https://github.com/jjoeldaniel}{\underline{github.com/jjoeldaniel }}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California State University, Fullerton}{Fullerton, CA}
      {Bachelor of Science in Computer Science}{Aug. 2022 -- May 2026}
    \resumeItem{\textbf{Relevant Coursework: }Data Structures, Algorithm Engineering, Operating Systems, Discrete Mathematics}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeProjectHeading
            {\textbf{Product Engineering Intern} $|$ {ESRI}}{May 2025 -- Present}
            \resumeItemListStart
              \resumeItem{Engineered a significant product enhancement by architecting and implementing R language support within ArcGIS Notebooks, utilizing a custom Docker image to create a scalable and robust runtime environment}
              \resumeItem{Spearheaded cross-functional initiatives by collaborating with senior engineers on technical design to define licensing and select core libraries for the new feature.}
    \resumeItemListEnd
    \resumeProjectHeading
            {\textbf{Supplemental Instructor} $|$ {CSU Fullerton}}{Aug. 2023 -- Present}
            \resumeItemListStart
              \resumeItem{Facilitated interactive and collaborative sessions to enhance students' comprehension of course material, resulting in a 10\% average grade increase}
              \resumeItem{Reinforced computer science fundamentals such as data structures, programming paradigms, and object oriented programming}
              \resumeItem{Collaborated with the program director and faculty liaison to develop strategies for effectively integrating SI and tutor support within lecture and lab structures.}
    \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Software Engineer Fellow} $|$ {Major League Hacking}}{June 2024 -- Aug. 2024}
          \resumeItemListStart
            \resumeItem{Contributed to Rust Analyzer, a Rust compiler front-end, by implementing a new client-side command to streamline the development workflow and improve codebase maintainability by removing outdated functionalities.}
            \resumeItem{Enhanced the new user experience by authoring comprehensive walkthrough and FAQ documentation to provide clear and accessible guidance.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Site Reliability Engineer Fellow} $|$ {Major League Hacking}}{June 2023 -- Sep. 2023}
          \resumeItemListStart
            \resumeItem{Engineered a full-stack, open-source website using Python, Flask, and MySQL, and established a complete CI/CD pipeline for automated deployments with Docker, Systemd, and shell scripting.}
            \resumeItem{Implemented comprehensive system monitoring by configuring Prometheus for data collection and Grafana for alerting and visualization as part of an intensive 12-week SRE curriculum.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Research Assistant} $|$ {CSU Fullerton}}{May 2023 -- August 2023}
          \resumeItemListStart
            \resumeItem{Developed an interactive website using the Mapbox API to visualize the correlation between foodborne illness outbreaks and geographical location.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
              {\textbf{Trends Analysis} $|$ \emph{Python, Rust}}{Jan. 2022 -- June 2023}
              \resumeItemListStart
                \resumeItem{Conducted a comprehensive analysis of user engagement by extracting data via the Discord API, identifying key trends in user activity, popular channels, and peak usage times.}
                \resumeItem{Leveraged a Bidirectional Encoder Representations from Transformers (BERT)  model to perform natural language processing on message content, successfully extracting relevant keywords and commonly used phrases.}
              \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Rust, C++, Java, Bash, JavaScript, TypeScript, SQL (Postgres, SQLite), R, HTML, CSS } \\
     \textbf{Tools}{: Git, Docker, Flask, FastAPI, Svelte, SvelteKit, Astro, Tailwind CSS} \\
    }}
 \end{itemize}

 %-----------EXTRACURRICULAR-----------
\section{Extracurricular}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Association For Computing Machinery (ACM) } $|$ \emph{President, Board Member}}{Aug. 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Oversaw all operations for a 2300-member organization, guiding a 50-person officer board to execute technical workshops, professional events, and community initiatives.}
            \resumeItem{Launched and managed the 'Node Buds' mentorship program, pairing over 50 students to foster skill development and increase member retention within the organization.}
            \resumeItem{Co-directed FullyHacks, securing 9 corporate sponsorships and managing event logistics for 400+ participants, achieving an 80\% retention rate over the two-day event.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
